\noindent
Auralization of road vehicles using spectral modeling synthesis\\
Master's Thesis in the \textsf{Master's Program in Sound and Vibration}\\
CHINMAY PENDHARKAR\\
Department of Civil and Environmental Engineering\\
Division of Applied Acoustics\\
Chalmers University of Technology\\

\vspace{1.5cm}
\section*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The LISTEN Project is collaborative project aiming to build a demonstrator software system for simulation and auralization of the sound environment of road and rail traffic of an urban area. The purpose of the demonstrator is to be able to listen to an urban soundscape at the planning stage, and also allow one to hear how noise prevention measures, such as a noise barrier, will affect the soundscape.

Auralization is used in the LISTEN project to simulate the desired soundscapes. The ability to recreate on-demand soundscapes of given environments allows designers to understand the limitations and practicalities of noise abatement and control.

This thesis looks at using Spectral Modeling Synthesis (SMS) to model vehicles as sound sources to be used in the auralization, along with outdoor sound propagation techniques, to allow simulation of urban soundscapes for the LISTEN project. The SMS technique has its roots in the computer music field, where it was originally used for digital creation of musical sounds using electronic synthesizers. The flexibility of this synthesis technique has allowed it to be used for modeling of various types of sound sources, including traffic and vehicle sounds for study of outdoor sound propagation.

This thesis implements and analyzes the use of SMS techniques for use in modeling road vehicle noise. The Analysis/Synthesis pair of operation defines the core of the SMS system, modeling and auralizing the sound respectively. The perceptual similarity between the original sound and the synthesized sound is also compared in a listening test for analysis of the use of this technique in  auralization of road vehicle sounds.

\vspace{\baselineskip}
\textbf{Keywords:} Outdoor Noise Propagation, Audio Synthesis, Spectral Modeling Synthesis, Auralization, Sonification, Sound Synthesis, LISTEN Project.


