%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

First and foremost I would like to thank my supervisor at Chalmers University of Technology,   Associate Professor Jens Forss\'{e}n for supporting me on this thesis work. I am thankful for the great help, advice and guidance he has given me over the course of the thesis work. His patience and steady support has been critical in helping me learn and understand more in the area of Auralization and outdoor noise propagation.

As this thesis work was a part of the LISTEN project, I would like to thank the members of the LISTEN project for giving me an opportunity to work with them and learn from their experience in this field. Specifically, I would like to thank Peter Lund\'{e}n at the Interactive Institute for his guidance on synthesis and auralization as well as Mats Nielsson at the G\"{o}sta Ekman Laboratory of Stockholm University for his advice on the design of the listening tests.

I would also like to thank the staff at the Division of Applied Acoustics at Chalmers University of Technology for the conducive and supportive environment I was given to focus on the thesis and also the resources that were needed for the thesis work and the listening tests.

Specifically within the Division of Applied Acoustics at Chalmers University of Technology, I would like to thank Penny Bergman for her help with the listening test data analysis, Professor Mendel Kleiner for his feedback and suggestion on the thesis work and Professor Wolfgang Kropp for his inspiration and guidance throughout the thesis work.

Finally, I really appreciate the help of fellow student of the Division of Applied Acoustics at Chalmers University of Technology on various topics through-out the thesis work through the form of arbitrary discussions or presentations. I also am very thankful to all my friends and other students at Chalmers University of Technology who helped with the listening test. 



